Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
minor, see if merged done
Dan text added, citations resolved

Prior work using small patches of chroma features includes ...
\cite{Casey2006,Ellis2007,Ellis2007a}.

@@

>>>>

Prior work using small patches of chroma features includes
the ``shingles'' of \cite{Casey2007}, which they used to
identify ``remixes'' i.e. music based on some of the same
underlying instrument tracks, as well as for matching
performances of Mazurkas \cite{Casey2008}.  That work,
however, was not concerned with extracting the deeper
common patterns underlying different pieces (and did not
use beat- or bar-synchronous features).  Earlier work in
beat-synchronous analysis includes \cite{Bartsch2001},
who looked for repeated patterns within single songs to
identify the chorus, and \cite{Ellis2007a}, who
cross-correlated beat-chroma matrices to match cover
versions of pop music tracks.  None of these works
examined or interpreted the content of the chroma
matrices in any detail.  In contrast, here we hope to
develop a codebook whose entries are of interest
in their own right.

@@

>>>>>>>>>>>>>>>>>>>> File 1
>>>>>>>>>>>>>>>>>>>> File 2
Crazy idea: chord recognition via quantization: transcribe codewords,
then just encode song to get chords. would this work?
>>>>>>>>>>>>>>>>>>>> File 3
<<<<<<<<<<<<<<<<<<<<
